---
title: "EEDA examples"
author: "Emile Latour"
date: '`r Sys.Date()`'
output: github_document
---

<!------ Thanks for any contributions! Please edit the .Rmd, the .md is a byproduct of the .Rmd! --------->

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  eval       = TRUE,    # whether to run code in code chunk
  echo       = TRUE,    # Whether to show code chunk in final output
  message    = FALSE,   # whether to preserve messages
  warning    = FALSE,   # whether to preserve warnings
  fig.width  = 6,       # consistent width for figures
  fig.height = 4,       # consistent height for figures
  out.width  = "100%",   # controls the output size
  fig.align  = "center" # give plot room to breathe
  )

#### Other options --------------------------------

## Scientific notation ---------------
# Turn off scientific notation
options(scipen = 999)


## define format ----------------
# If you don't define format here, you'll need put `format = "html"` in 
# every kable function.
options(knitr.table.format = "html")  # use this option when knitting html
# options(knitr.table.format = "latex")  # use this option when knitting pdf


## Define the repository for packages ----------------

options(repos = c(CRAN = "http://cran.rstudio.com"))


#### Packages --------------------------------------

# This is where we load in all the packages we plan to use

# universally useful packages
if (!require("pacman")) install.packages("pacman")
if (!require("devtools")) install.packages("devtools")

# github packages
if (!require("janitor")) devtools::install_github("sfirke/janitor")
if (packageVersion("janitor") < "0.4.0.9000") {
  devtools::install_github("sfirke/janitor")
}
  
# Load the list of packages
pacman::p_load(
  tidyverse,     # packages ggplot2, tibble, tidyr, readr, purrr, and dplyr 
  forcats,       # functions for factors, forcats is an anagram for factors
  broom,         # functions tidy(), glance(), augment()
  magrittr,      # includes the %<>% assignment-pipe (%>% is loaded from dplyr)
  rlang,         # For use in tidyevaluation
  janitor,       # for working with dirty data
  lubridate,     # for working with dates and times
  stringr,       # handy string operations
  knitr,         # A General-Purpose Package for Dynamic Report Generation in R
  kableExtra,    # Enahced table functions
  ggthemes,      # Extra Themes, Scales and Geoms for 'ggplot2'
  scales,        # Scale Functions for Visualization
  ggpubr,        # Customizing ‘ggplot2’- based publication ready plots
  here           # Constructs paths to your project's files

  )

```

# Load the script for the EEDA plots

```{r}
source(
  here::here("make-eeda-plots.R")
  )

```

# Examples of `plot_cont()`

The `plot_cont()` function will plot a histogram and table of summary statistics for __continuous__ variables. As one of the inputs, the user can specify the method to use for creating histogram bins.

Below are some examples using the `mtcars` data set.

```{r}
plot_cont(data = mtcars, var = disp)
plot_cont(data = mtcars, var = disp, binw_select = "Sturges")
plot_cont(data = mtcars, var = disp, binw_select = "Scott")
plot_cont(data = mtcars, var = disp, binw_select = "Hadley")

```

# Examples of `plot_categ()`

The `plot_categ()` function creates a bar plot and frequency table for __categorical__ variables.

Here is an example using the the `mtcars` data set once again.

```{r}
mt2 <- mtcars %>% 
  mutate(cyl = factor(cyl))

plot_categ(data = mt2, var = cyl)

```

Or another using th `iris` data set.

```{r}
plot_categ(data = iris, var = Species)
```



# Example of `make_plots()`

The `make_plots()` function takes a data set as an input and, depending on the variable class, will apply either `plot_cont()` or `plot_categ()`. 

An example using the `diamonds` data set fromm the `ggplot2` package.

```{r}
make_plots(data = diamonds)

```

Note that all three functions are pipeable using `dplyr`. So if instead of the entire data set, you wanted to plot a subset:

```{r}
diamonds %>% 
  dplyr::select(carat, color, clarity, price) %>% 
  make_plots(.)
```

